\subsection{Stone Duality}
This section of the appendix gives a more algebraic way of 
constructing Stone spaces.

\begin{dfn}[A Boolean algebra on $F(\Si,n)$]
    Let $T$ be a $\Si$-theory.
    We quotient out $F(\Si,n)$ by the equivalence relation
    \[  
        \phi \sim \psi \quad := 
        \quad \phi \text{ and } \psi \text{ equivalent modulo } T
        := T \model{\Si} \forall v, (\phi \IFF \psi)
    \]
    Call the projection into the quotient $\pi$
    and the quotient $F(\Si,n) / T$.
    We make $F(\Si,n) / T$ into a Boolean algebra by 
    interpreting $0$ as $\pi(\bot)$, $1$ as $\pi(\top)$, 
    $\pi(\phi) \sqcap \pi(\psi)$ as $\pi(\phi \AND \psi)$,
    $\pi(\phi) \sqcup \pi(\psi)$ as $\pi(\phi \OR \psi)$,
    $- \pi(\phi)$ as $\pi(\NOT \phi)$ and 
    $\pi(\phi) \leq \pi(\psi)$ as 
    \[\set{(\pi(\phi),\pi(\psi)) \st T \model{\Si} \forall v, (\phi \to \psi)}\]
    One can verify that these are well-defined and satisfy the axioms of 
    a Boolean algebra.
    Notice we need $T$ (potentially chosen to be the empty set) 
    to make $\to$ look like $\leq$ and that we had to quotient modulo $T$ 
    to make $\leq$ satisfy antisymmetry. 
    Antisymmetry in this context looks very much like 
    `propositional extensionality'.
    Thus it makes sense to consider the Stone space of this Boolean algebra 
    $S(F(\Si,n) / T)$.
\end{dfn}

\begin{lem}
    \link{technical_lem_max_subs_pullback}
    If $p \subs F(\Si,n)$ is a maximal subset 
    ($\forall \phi \in F(\Si,n), \phi \in p$ or $\NOT \phi \in p$) then 
    $\pi(\phi) \in \pi(p)$ in the quotient implies $\phi \in p$.
\end{lem}
\begin{proof}
    If $\pi(\phi) \in \pi(p)$ then there exists $\psi \in p$ such that 
    $\psi$ is equivalent to $\phi$ modulo $T$.
    By consistency with $T$ there exists a non-empty $\Si$-model $\MM$ of $T$
    and $b \in {\MM}^n$ 
    such that $\MM \model{\Si} p(b)$, 
    in particular $\MM \model{\Si} \psi(b)$.
    Equivalence modulo $T$ then gives us that $\MM \model{\Si} \phi(b)$.
    By maximality of $p$, 
    $\phi$ or $\NOT \phi$ is in $p$ but the latter would lead to 
    $\MM \nodel{\Si} \phi(b)$, 
    a contradiction.
\end{proof}

\begin{prop}[The Stone space is a set of ultrafilters]
    The Stone space of a $\Si$-theory $T$ is homeomorphic 
    to the set of ultrafilters from $S(F(\Si,n) / T)$ 
    that have preimage consistent with $T$ with the subspace topology.
    In other words, if $\pi$ is the projection to the quotient then
    $S_n(T) \iso X$, where
    \[X := 
    \set{\FF \in S(F(\Si,n) / T) \st \pi^{-1}(\FF) \text{ consistent with } T}\]
\end{prop}
\begin{proof}
    Warning: this proof uses $\pi$ to be three different things,
    the quotient $F(\Si,n) \to F(\Si,n) / T$, 
    the image map (of the quotient) $S_n(T) \to X$, 
    and the map of clopen sets (the image map of the image map) 
    $\PP(S_n(T)) \to \PP(X)$.
    The second will be a homeomorphism and the third will be a map between
    subsets of the topologies (in particular the clopen subsets).

    We show that sending $p \in S_n(T)$ to its image under the projection 
    to the quotient $\pi(p)$ is a homeomorphism.
    To show that it is well-defined it suffices to show that for any $p$, a 
    maximal $n$-type over $T$, $\pi(p)$ is an ultrafilter of $F(\Si,n) / T$
    with preimage consistent with $T$.
    Preimage being consistent with $T$ 
    follows from the definition of $n$-types over theories.
    To show that it is a proper filter:
    \begin{itemize}
        \item $\top \in p$ by consistency and maximality. 
            Hence $\pi(\top) \in \pi(p)$.
        \item If $\pi(\bot) \in \pi(p)$ then
            \linkto{technical_lem_max_subs_pullback}{$\bot \in p$} 
            which is a contradiction with consistency.
        \item If $\pi(\phi), \pi(\psi) \in \pi(p)$ then 
            \linkto{technical_lem_max_subs_pullback}{$\phi,\psi \in p$} and so
            $\phi \AND \psi \in p$ thus by definition of the Boolean algebra 
            $F(\Si,n) / T$, 
            \[\pi(\phi) \sqcap \pi(\psi) = \pi(\phi \AND \psi) \in \pi(p)\]
        \item If $\pi(\phi) \in \pi(p)$ and $\pi(\phi) \leq \pi(\psi)$ then 
            \linkto{technical_lem_max_subs_pullback}{$\phi \in p$} 
            and by definition of $\leq$,
            \[T \model{\Si} \forall v, (\phi \to \psi)\]
            Since $p$ is consistent with $T$ there exists a non-empty
            $\Si$-structure $\MM$ and $b \in {\MM}^n$ such that 
            $\MM \model{\Si} \phi(b) \to \psi(b)$ and $\MM \model{\Si} \phi(b)$.
            Hence $\MM \model{\Si} \psi(b)$ and by maximality of $p$ we have 
            $\psi \in p$ and $\pi(\psi) \in \pi(p)$.
    \end{itemize}
    The image $\pi(p)$ is an ultrafilter by the 
    \linkto{negation_is_in_ultrafilter}{equivalent definition}:
    if $\pi(\phi) \in F(\Si,n) / T$ then either 
    $\phi \in p$ or $\NOT \phi \in p$ by maximality of $p$, 
    hence $\pi(\phi) \in \pi(p)$ or $\pi(\NOT \phi) \in \pi(p)$.
    Thus we have $\pi$ is a map into \[
    \set{\FF \in S(F(\Si,n) / T) \st \pi^{-1}(\FF) \text{ consistent with } T}\]

    Injectivity: if $p,q \in S_n(T)$ and $\pi(p) = \pi(q)$ then 
    if $\phi \in p$, we have $\pi(\phi) \in \pi(p) = \pi(q)$ and by our 
    claim above $\phi \in q$.
    Surjectivity: let $\FF \in S(F(\Si,n) / T)$ 
    have its preimage consistent with $T$.
    Then its preimage is an $n$-type.
    If its preimage is a maximal $n$-type then we have surjectivity.
    Indeed since $\FF$ is an ultrafilter if $\phi \in F(\Si,n)$ then 
    $\pi(\phi) \in \FF$ or $\pi(\NOT \phi) = - \pi(\phi) \in \FF$,
    hence $\phi \in \pi^{-1}(\FF)$ or $\NOT \phi \in \pi^{-1}(\FF)$.

    To show that the map is continuous in both directions,
    it suffices to show that images of clopen sets are clopen and preimages of 
    clopen sets are clopen,
    as each topology is generated by their clopen sets.
    For $\phi \in F(\Si,n)$ since 
    $\pi : S_n(T) \to X$ is a bijection we have that
    \[\pi([\phi]_T) = \set{\FF \in X \st \phi \in \pi^{-1}(\FF)} =
    \set{\FF \in F(\Si,n) / T \st \pi(\phi) \in \FF \text{ and } \FF \in X} = 
    [\pi(\phi)] \sqcap X\]
    and similarly $\pi^{-1}([\pi(\phi)] \sqcap X) = [\phi]_T$.
    Hence there is a correspondence between clopen sets.
\end{proof}

\begin{lem}[Topological consistency]
    \link{topological_consistency}
    Let $\FF \in S(F(\Si,n) / T)$ and $T$ be a $\Si$-theory.
    $\pi^{-1}(\FF)$ is consistent with $T$ if and only if 
    \[\pi^{-1}(\FF) \in \bigcap_{\phi \in \pi^{-1}(\FF)} [\phi]_T\]
    if and only if 
    \[\bigcap_{\phi \in \pi^{-1}(\FF)} [\phi]_T \text{ is non empty}\]
\end{lem}
\begin{proof}
    ($1. \implies 2. \implies 3.$)
        Suppose $\pi^{-1}(\FF)$ is consistent with $T$.
        Then $\pi^{-1}(\FF) \in S_n(T)$ thus for any $\phi \in \pi^{-1}(\FF)$, 
        $\pi^{-1}(\FF) \in [\phi]_T$. 
        Hence 
        \[\pi^{-1}(\FF) \in \bigcap_{\phi \in \pi^{-1}(\FF)} [\phi]_T\]
        and it is non-empty.

    ($3. \implies 1.$)
        Suppose 
        \[p \in \bigcap_{\phi \in \pi^{-1}(\FF)} [\phi]_T\]
        then $\forall \phi \in \pi^{-1}(\FF), \phi \in p$.
        As $\FF$ is an ultrafilter, for any $\phi \in p$, 
        \[\phi \notin \pi^{-1}(\FF) \implies \NOT \phi \in \pi^{-1}(\FF) 
        \implies \NOT \phi \in p \text{ a contradiction}\]
        Hence $p = \pi^{-1}(\FF)$.
        Hence $\pi^{-1}(\FF) \in S_n(T)$ and thus is consistent with $T$.
\end{proof}

\begin{prop}[Topological compactness implies compactness for types]
    \link{compactness_for_types_2}
    Let $\FF \in S(F(\Si,n)/T)$ and $T$ be a $\Si$-theory.
    Then $\pi^{-1}(\FF)$ is consistent with $T$ 
    if and only if $\pi^{-1}(\FF)$ if finitely consistent
    with $T$.
\end{prop}
\begin{proof}
    By definition $\pi^{-1}(\FF)$ is finitely consistent with $T$ if and only if 
    any finite subset of $\pi^{-1}(\FF)$ is consistent with $T$.
    Translating this to the topology, this is
    \linkto{topological_consistency}{if and only if} 
    for any finite subset $\De \subs \pi^{-1}(\FF)$,
    \[\bigcap_{\phi \in \De} [\phi]_T \text{ is non empty}\]
    By \linkto{stone_of_theo_compact}{topological compactness of $S_n(T)$} 
    this is if and only if 
    \[\bigcap_{\phi \in \pi^{-1}(\FF)} [\phi]_T \text{ is non empty}\]
    \linkto{topological_consistency}{Translating this back to model theory}
    this is if and only if $\pi^{-1}(\FF)$ is consistent with $T$.
\end{proof}